Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)

### 2022-01-14 docs/manuscript/manuscript.tex
update: revisions following feedback from meta-psychology

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
  pdfauthor={Brad McKay1 \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Meta-science; GRIMMER; Effect sizes; Perceptual motor learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Commentary on Lola \& Tzetzis papers}
\keywords{Meta-science; GRIMMER; Effect sizes; Perceptual motor learning}
\usepackage{lineno}

@@

\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
\date{}

@@

\abstract{
We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all six articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000. Impossible statistics were reported in four out of the six articles. Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects. The results reported in the six articles in question are unreliable. Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.
}

@@

We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola, Giatis, Pérez-Turpin, \& Tzetzis, In Press; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015). All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. We will refer to the six articles throughout this paper using the following numbering system:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Lola, A.C., \& Tzetzis, G.C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. \emph{International Journal of Sport and Exercise Psychology}, 1-21. \url{https://doi.org/10.1080/1612197X.2021.1877325}
\item
  Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C. (In Press). The influence of analogies on the development of selective attention in novices in normal or stressful conditions. \emph{Journal of Human Sport and Exercise}. \url{https://doi.org/10.14198/jhse.2023.181.12}
\item
  Lola, A.C., \& Tzetzis, G.C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. \emph{Journal of Physical Education and Sport}, 20(5), 2478-2486. \url{https://doi.org/10.7752/jpes.2020.05339}
\item
  Tzetzis, G.C., \& Lola, A.C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. \emph{International Journal of Sport Psychology}, 46(2), 152-166. \url{https://doi.org/10.7352/IJSP.2015.46.152}
\item
  Lola, A.C., \& Tzetzis, G.C., \& Zetou, H. (2012). The effect of implicit and explicit practice in the development of decision making in volleyball serving. \emph{Perceptual and Motor Skills}, 114(2), 665-678. \url{https://doi.org/10.2466/05.23.25.PMS.114.2.665-678}
\item
  Tzetzis, G.C., \& Lola, C.A. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions. \emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This article is in a journal of a publishing group that has been identified as a potential predatory journal. Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/publication/341001393_THE_ROLE_OF_IMPLICIT_EXPLICIT_INSTRUCTION_AND_THEIR_COMBINATION_IN_LEARNING_ANTICIPATION_SKILL_UNDER_NORMAL_AND_STRESS_CONDITIONS}). In fact, the earliest available issue on the journal's webpage is from 2016.}
\end{enumerate}

@@

\caption{\label{tab:table1}Participant demographics in each of the target articles.}
\fontsize{11}{13}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{ll}
\toprule
Target article & Sample size and participant details\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 1}}\\
\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 2}}\\
\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 3}}\\
\hspace{1em}Lola \& Tzetzis (2020) & 80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 4}}\\
\hspace{1em}Tzetzis \& Lola (2015) & 60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 5}}\\
\hspace{1em}Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 6}}\\
\hspace{1em}Tzetzis \& Lola (2010) & 48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note.} 
\item[a] Articles 1,3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 2 from Articles 1 and 3, and a different age range in Article 3 from Articles 1 and 2.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized. All six articles involved female children learning a volleyball skill as part of a volleyball camp. In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand. The purpose of all six experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice. Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test. The authors also included a high stress test in Articles 1, 2 and 6.

@@

The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and 5), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3). In addition, Articles 1 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale. Articles 1, 4, 5, and 6 also analyzed the number of explicit rules recalled.

@@

None of the six articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 10, 2021) the corresponding author for Article 1 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent and presumably, all planned analyses had been completed. After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication about our concerns regarding the data irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 1, but for the most part only provided more general responses to our concerns. Interestingly, parts of their responses were inaccurate relative to information in the target articles---increasing our concerns about these articles. The authors did admit that some of the values reported in the target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data \emph{and} analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: \url{https://osf.io/raz6q/}.

@@

Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity. Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion). Conventional benchmarks for small, medium, and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions). Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).

To evaluate the maximum range of plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}). We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation. The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97. In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature. The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.

@@

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1}

@@

\caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of \(d\) = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
\end{figure}

In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes. In Article 1, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article. The smallest post-intervention effect at any of the three time points was \emph{d} = 286.42, while the largest effect was \emph{d} = 3504.86. A similar picture emerges when analyzing the accuracy data. All the pre-test differences were improbably large (all \emph{d}'s \(\geq\) 2.52) despite being reported as not significantly different in the articles. Ten of the pairwise comparisons resulted in \emph{d}'s \(\geq\) 100 following treatment with the independent variables. The motor component data revealed post-treatment effect sizes ranging from \emph{d} = 1.16 to \emph{d} = 13.5.
In Article 2, the smallest post-intervention difference in reaction times was \emph{d} = .64. However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41. The accuracy data also reflect improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35.

@@

In Article 1, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants. Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item. At each of the three low-stress time points, the means reported for all four groups ranged from 1.02 to 1.09. During the high-stress time point, the means ranged from 3.95 to 4.09. The means for two groups were reported as greater than 4, which is not possible given the maximum score on the Competitive State Anxiety Inventory-2 is 4.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)},
  pdfauthor={Brad McKay1 \& Michael J. Carter1},
  pdflang={en-EN},
  pdfkeywords={Metascience; GRIMMER; Effect sizes; Perceptual motor learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Commentary on Lola \& Tzetzis papers}
\keywords{Metascience; GRIMMER; Effect sizes; Perceptual motor learning}
\usepackage{lineno}

@@

\title{Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)}
\author{Brad McKay\textsuperscript{1} \& Michael J. Carter\textsuperscript{1}}
\date{}

@@

\abstract{
We present a critical re-analysis of six implicit learning papers published by the same authors between 2010 and 2021. We calculated effect sizes for each pairwise comparison reported in the papers using the data published in each article. We further identified mathematically impossible data reported in multiple papers, either with deductive logic or by conducting a GRIMMER analysis of reported means and standard deviations. We found the pairwise effect sizes were implausible in all six articles in question, with Cohen's \emph{d} values often exceeding 100 and sometimes exceeding 1000. \textcolor{red}{In contrast, the largest effect size observed in a million simulated experiments with a true effect of} \emph{d} \textcolor{red}{= 3 was} \emph{d}\textcolor{red}{ = 6.6.} Impossible statistics were reported in four out of the six articles. Reported test statistics and \(\eta^{2}\) values were also implausible, with several \(\eta^{2}\) = .99 and even \(\eta^{2}\) = 1.0 for between-subjects main effects. The results reported in the six articles in question are unreliable. Many of the problems we identified could be spotted without further analysis, highlighting the need for adequate statistical training in the field of motor learning.
}

@@

We reanalyzed six articles by Afroditi Lola, George Tzetzis, and their colleague (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021; Lola \& Tzetzis, 2020, 2021; Lola, Tzetzis, \& Zetou, 2012; Tzetzis \& Lola, 2010, 2015). All six papers described experiments that sampled young females who were enrolled in a volleyball camp (see Table \ref{tab:table1}). In their experiments, the authors investigated the effects of implicit and explicit instructions on learning motor and perceptual skills. Our reanalysis of the target articles evaluated the plausibility of the reported means, standard deviations, and test statistics. We will refer to the six articles throughout this paper using the following numbering system:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Lola, A.C., Giatsis, G., Pérez-Turpin, J.A., \& Tzetzis, G.C. (2021). The influence of analogies on the development of selective attention in novices in normal or stressful conditions. \emph{Journal of Human Sport and Exercise}. \url{https://doi.org/10.14198/jhse.2023.181.12}
\item
  Lola, A.C., \& Tzetzis, G.C. (2021). The effect of explicit, implicit and analogy instruction on decision making skill for novices, under stress. \emph{International Journal of Sport and Exercise Psychology}, 1-21. \url{https://doi.org/10.1080/1612197X.2021.1877325}
\item
  Lola, A.C., \& Tzetzis, G.C. (2020). Analogy versus explicit and implicit learning of a volleyball skill for novices: The effect on motor performance and self-efficacy. \emph{Journal of Physical Education and Sport}, 20(5), 2478-2486. \url{https://doi.org/10.7752/jpes.2020.05339}
\item
  Tzetzis, G.C., \& Lola, A.C. (2015). The effect of analogy, implicit, and explicit learning on anticipation in volleyball serving. \emph{International Journal of Sport Psychology}, 46(2), 152-166. \url{https://doi.org/10.7352/IJSP.2015.46.152}
\item
  Lola, A.C., \& Tzetzis, G.C., \& Zetou, H. (2012). The effect of implicit and explicit practice in the development of decision making in volleyball serving. \emph{Perceptual and Motor Skills}, 114(2), 665-678. \url{https://doi.org/10.2466/05.23.25.PMS.114.2.665-678}
\item
  Tzetzis, G.C., \& Lola, C.A. (2010). The role of implicit, explicit instruction and their combination in learning anticipation skill, under normal and stress conditions. \emph{International Journal of Sport Sciences and Physical Education}, 1, 54-59.\footnote{This article is in a journal of a publishing group that has been identified as a potential predatory journal. Further, we were unable to find an archived version of this article on the journal's webpage and were only able to find a posted version on ResearchGate (\url{https://www.researchgate.net/profile/Angela-Calder/publication/234000504_The_scientific_basis_for_recovery_training_practices_in_sport/links/5428fff80cf26120b7b574ad/The-scientific-basis-for-recovery-training-practices-in-sport.pdf\#page=57}). In fact, the earliest available issue on the journal's webpage is from 2016.}
\end{enumerate}

@@

\caption{\label{tab:table1}Participant demographics in each of the target articles.}
\fontsize{11}{13}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{ll}
\toprule
Target article & Sample size and participant details\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 1}}\\
\hspace{1em}Lola et al (2021) & 60 females, age range: 11 to 12 years ($M_{age}$ and SD not reported)\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 2}}\\
\hspace{1em}Lola \& Tzetzis (2021) & 60 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 3}}\\
\hspace{1em}Lola \& Tzetzis (2020) & 80 females, age range: 10 to 11 years ($M_{age}$ = 10.48, SD = 0.911)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 4}}\\
\hspace{1em}Tzetzis \& Lola (2015) & 60 females, age range: 9 to 12 years ($M_{age}$ = 10.48, SD = 0.91)\textsuperscript{a}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 5}}\\
\hspace{1em}Lola et al (2012) & 60 females, age range: 10 to 12 years ($M_{age}$ = 11.2, SD = 0.3)\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Article 6}}\\
\hspace{1em}Tzetzis \& Lola (2010) & 48 females, age range: 12 to 13 years ($M_{age}$ = 12.38, SD = 0.34)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note.} 
\item[a] Articles 2, 3 and 4 report identical means and standard deviations for the age of their participants despite a different sample size in Article 3 from Articles 2 and 4, and a different age range in Article 4 from Articles 2 and 3.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

Although there were some differences between the reported experiments in the target articles, there were many methodological commonalities that can be summarized. All six articles involved female children learning a volleyball skill as part of a volleyball camp. In each case, the participants were reported to have minimal experience (i.e., were described as novices) with the task at hand. The purpose of all six experiments was to evaluate perceptual or motor learning differences as a function of the type of instruction received during practice. Each experiment included a pre-test, an acquisition (i.e., practice) phase involving 12 sessions spaced over four weeks, and a post-test. The authors also included a high stress test in Articles 1 (Lola, Giatis, Pérez-Turpin, \& Tzetzis, 2021), 2 (Lola \& Tzetzis, 2021) and 6 {[}Tzetzis and Lola (2010)\}.

@@

The primary outcome measures used in these experiments were reaction time (Articles 1, 2, 4, 5, and \textcolor{red}{6}), response accuracy (Articles 1, 2, 4, and 5), and motor performance measured on a 4-point scale (Article 3). In addition, Articles 2 and 6 included a measure of state anxiety, the Competitive State Anxiety Inventory-2 (Tsorbatzoudis, Barkoukis, Kaissidis-Rodafinos, \& Grouios, 1998), and Article 3 had a measure of self-efficacy using a Likert scale. Articles 2, 4, 5, and 6 also analyzed the number of explicit rules recalled.

@@

None of the six articles in question included a link to a public repository where the data could be accessed. We first wrote (email sent February 10, 2021) the corresponding author for Article 2 and asked if they would be willing to share the data for this experiment. The authors' response was that the data could not be shared as they were not finished with their analyses and were in the process of running different tests (A. Lola, personal communication, February 12 2021). We followed up this email (sent February 12 2021) by asking whether they would instead be willing to share the data from Articles 3-6 as these articles were less recent, and presumably all planned analyses had been completed. After a 2 week period with no response, we followed up with a third email (sent February 26 2021) and reiterated our interest in obtaining their data from Articles 3-6. The authors' response was that they were unable to share data from any of these articles because in some cases they no longer had the data and in other cases they had plans to conduct further analyses (A. Lola, personal communication, March 2 2021).

Our first two requests did not include any indication about our concerns regarding the data irregularities. Subsequently, in a fourth email (sent April 12 2021) we outlined our concerns for each article\footnote{Excluding Lola, Giatis, Pérez-Turpin, and Tzetzis (2021) article as it had not yet been accepted for publication.} and once again reiterated our request to the authors to share any available data for any of the target articles. These requests were once again refused. The authors did address some specific concerns regarding Article 2, but for the most part only provided more general responses to our concerns. The authors admitted that some of the values reported in the other target articles were incorrect but did not identify which values or articles. Despite this, the authors maintained that the data irregularities---identified in our email and described in this paper---do not impact the veracity of their analyses or conclusions (A. Lola, personal communication, April 22 2021). We illustrate below that the data \emph{and} analyses reported in each of the articles reviewed are unreliable. Our extracted data and analysis scripts can be accessed at the following link: \url{https://osf.io/raz6q/}.

@@

Cohen's \emph{d} is used to describe the standardized mean difference of an effect and values can range between 0 and infinity \textcolor{red}{in both the negative and positive direction. We calculated absolute values so that all effects were positive}. Cohen's \(d_{s}\) (Cohen, 1988) is the observed difference between group means divided by their pooled standard deviation (see Lakens, 2013 for a detailed discussion). Conventional benchmarks for small, medium, and large effects are \emph{d} = .2, .5, and .8, respectively (Cohen, 1962); however, this \emph{cargo-cult} approach to effect size interpretation has been heavily discouraged (see Correll, Mellinger, McClelland, \& Judd, 2020; Field, 2016; Lakens, 2013; Thompson, 2007 for discussions). Recently, an analysis of 6447 Cohen's \emph{d} statistics extracted from social psychology meta-analyses observed median and 75th percentile Cohen's \emph{d} values of .36 and .65, respectively---suggesting the conventional benchmarks may overestimate typical effects (Lovakov \& Agadullina, 2021).\textcolor{red}{In the field of motor learning, recent meta-analyses have found average effect sizes in the published literature of} \emph{d} = .19 (McKay et al., 2021), \emph{d}= .54 (McKay, Yantha, Hussien, Carter, \& Ste-Marie, in press), and \emph{d} = .71 (Lohse, Buchanan, \& Miller, 2016).

To evaluate the maximum plausible Cohen's \emph{d} statistics one might encounter from experiments similar to those reported in the target Articles, we conducted two simulations that each consisted of one million experiments (see Figure \ref{fig:fig1}). We set the true effect size at \emph{d} = .8, the conventional benchmark for a ``large'' treatment effect, in the first simulation. The largest effect size observed from the one million simulated experiments was \emph{d} = 2.97. In the second simulation, we set the true effect size at \emph{d} = 3, an unrealistically large effect size that might rarely be encountered in the psychology and/or motor learning literature. The maximum effect size observed in the one million simulated experiments was \emph{d} = 6.6.

@@

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{../../figs/fig1b}

@@

\caption{Absolute Cohen's \(d\) estimates from Articles 1-5 plotted on a logarithmic scale. Only data from the original tables in Article 2 are included. All pairwise comparisons have been included for all dependent measures in each experiment. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = .8 is illustrated by shaded green and blue regions of the figure, reaching a maximum value of \(d\) = 2.97. The range of observed values from a simulation of 1,000,000 experiments with a true effect of \(d\) = 3 is illustrated by the shaded purple and blue regions of the figure, reaching a maximum value of \(d\) = 6.6.}\label{fig:fig1}
\end{figure}

In the context of the maximum values observed in our simulations, all six articles in question reported implausibly large effect sizes. \textcolor{red}{The original table of summary statistics in Article 1 indicated that} the smallest post-intervention difference in reaction times was \emph{d} = .64. However, all other effects were larger than \emph{d} = 8.7 and the largest effect was \emph{d} = 41. The accuracy data also reflected improbably large post-intervention differences, with two-thirds of all comparisons showing effects larger than \emph{d} = 5 and a largest effect of \emph{d} = 13.35. \textcolor{red}{However, a correction to the tables of summary statistics was published that included substantially smaller standard deviations than the original tables. While the updated data do imply smaller effect sizes, as we discuss below, they appear to be inconsistent with the analyses reported in Article 2.}

In Article 2, the smallest pre-test difference for reaction time was \emph{d} = 1.29 and the largest pre-test difference was \emph{d} = 35.32---although none of the groups were reported as significantly different in the article. The smallest post-intervention effect at any of the three time points was \emph{d} = 286.42, while the largest effect was \emph{d} = 3504.86. A similar picture emerges when analyzing the accuracy data. All the pre-test differences were improbably large (all \emph{d}'s \(\geq\) 2.52) despite being reported as not significantly different in the articles. Ten of the pairwise comparisons resulted in \emph{d}'s \(\geq\) 100 following treatment with the independent variables. The motor component data revealed post-treatment effect sizes ranging from \emph{d} = 1.16 to \emph{d} = 13.5.

@@

In Article 2, the Competitive State Anxiety Inventory-2 was used to assess the level of cognitive and somatic stress experienced by participants. Responses were measured on a Likert scale ranging from 1 to 4 with the data appearing to represent the average response per item. At each of the three low-stress time points, the means reported for all four groups ranged from 1.02 to 1.09. During the high-stress time point, the means ranged from 3.95 to 4.09. The means for two groups were reported as greater than 4, which is not possible given the maximum score on the Competitive State Anxiety Inventory-2 is 4.
